Transparent Standby for Low-Power, Resource-Constrained Embedded Systems

### 2018-05-29 LCTES/lctes.tex
(*) fix previous commit
(>) LCTES

\documentclass[sigplan]{acmart}

@@

%%% If you see 'ACMUNKNOWN' in the 'setcopyright' statement below,
%%% please first submit your publishing-rights agreement with ACM (follow link on submission page).
%%% Then please update our instructions page and copy-and-paste the NEW commands into your article.
%%% Please contact us in case of questions; allow up to 10 min for the system to propagate the information.
%%%
%%% The following is specific to LCTES'18 and the paper
%%% 'Transparent Standby for Low-Power, Resource-Constrained Embedded Systems: A Programming Language-Based Approach (Short WIP Paper)'
%%% by Francisco Sant'Anna, Alexandre Sztajnberg, and Noemi Rodrigues.
%%%
%\setcopyright{ACMUNKNOWN}
\setcopyright{acmcopyright}
\acmPrice{15.00}
\acmDOI{10.1145/3211332.3211337}
\acmYear{2018}
\copyrightyear{2018}
\acmISBN{978-1-4503-5803-3/18/06}
\acmConference[LCTES'18]{19th ACM SIGPLAN/SIGBED Conference on Languages, Compilers, and Tools for Embedded Systems}{June 19--20, 2018}{Philadelphia, PA, USA}

\begin{document}
%\title{A Language-Based Approach for Standby in Embedded Systems}
\title{WIP: Transparent Standby for Low-Power, Resource-Constrained Embedded Systems}
\subtitle{A Programming Language-Based Approach}

@@

\author[F.~Sant'Anna]{Francisco Sant'Anna}
\email{francisco@ime.uerj.br}
\affiliation{Rio de Janeiro State University, Brazil}
%
\author[A.~Sztajnberg]{Alexandre Sztajnberg}
\email{alexszt@ime.uerj.br}
\affiliation{Rio de Janeiro State University, Brazil}
%
\author[A.L..~de~Moura]{Ana L\'ucia de Moura}
\email{amoura@inf.puc-rio.br}
\affiliation{PUC-Rio, Brazil}
%
\author[N.~Rodrigues]{Noemi Rodrigues}
\email{noemi@inf.puc-rio.br}
\affiliation{PUC-Rio, Brazil}

>>>>

\documentclass[sigplan,screen]{acmart}

@@

%%% The following is specific to LCTES'18 and the paper
%%% 'Transparent Standby for Low-Power, Resource-Constrained Embedded Systems: A Programming Language-Based Approach (Short WIP Paper)'
%%% by Francisco Sant'Anna, Alexandre Sztajnberg, and Noemi Rodrigues.
%%%
\setcopyright{acmcopyright}
\acmPrice{15.00}
\acmDOI{10.1145/3211332.3211337}
\acmYear{2018}
\copyrightyear{2018}
\acmISBN{978-1-4503-5803-3/18/06}
\acmConference[LCTES'18]{19th ACM SIGPLAN/SIGBED Conference on Languages, Compilers, and Tools for Embedded Systems}{June 19--20, 2018}{Philadelphia, PA, USA}

\begin{document}
%\title{A Language-Based Approach for Standby in Embedded Systems}
\title[Transparent Standby for Low-Power, Resource-Constrained ...]{Transparent Standby for Low-Power, Resource-Constrained Embedded Systems}
\subtitle{A Programming Language-Based Approach (Short WIP Paper)}

@@

\author[F.~Sant'Anna]{Francisco Sant'Anna}
\affiliation{Rio de Janeiro State University, Brazil}
\email{francisco@ime.uerj.br}
%
\author[A.~Sztajnberg]{Alexandre Sztajnberg}
\affiliation{Rio de Janeiro State University, Brazil}
\email{alexszt@ime.uerj.br}
%
\author[A.L.~de~Moura]{Ana L\'ucia de Moura}
\affiliation{PUC-Rio, Brazil}
\email{amoura@inf.puc-rio.br}
%
\author[N.~Rodrigues]{Noemi Rodrigues}
\affiliation{PUC-Rio, Brazil}
\email{noemi@inf.puc-rio.br}
